Near Optimal Behavior with Approximate State Abstraction

### 2016-02-03 paper/results_discussion.tex

\section{Approximate Abstraction on Example Domains}

%Explanation of what abstraction is used
We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP. More specifically, we relate $\epsilon$ to:
\begin{equation}
|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
\end{equation}
For different values of $\epsilon$.

\dnote{Also put in a note that we're using a uniform weighting scheme}
\enote{Also put in a note how we're randomly choosing a Q*}
%Explain plots
Here we discuss the results shown in states blah blah \dnote{Description of this section}.

@@

% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. Value for all four sample domains.
\begin{figure}
\centering

@@

\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}
}

@@

\label{fig:main_empirical_results}
\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
\end{figure}

>>>>

\section{Approximate Abstraction on Example Domains}
%Explanation of what abstraction is used
We run experiments on aggregation functions the $\ep{Q^*}$ abstraction. For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\ep{Q^*}$ criteria. The order in which ground states are selected and then greedily added is randomized so there is randomization across trials. Every ground state is equally weighted in its abstract state.

%Explanation of what plots done
For each domain we report two quantities as a function of epsilon in Figures \ref{fig:main_empirical_results1} and \ref{fig:main_empirical_results2}. First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$. The smaller this value, the smaller the state space of the $\ac{MDP}$ that the agent must plan over. Second, we report the value under the abstract policy of the initial ground state. 50 Trials are gathered for each data point \enote{except ones where it doesn't matter (nChain and Minefield) -- is this worth noting?}

@@

\enote{Should we regenerate plots for nChain so it has CIs to match other plots?}
% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.
\begin{figure}
\label{fig:main_empirical_results1}
\centering

@@

\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
\end{figure}

% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For Taxi and Random.
\begin{figure}
\label{fig:main_empirical_results2}
\centering
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}
}

@@

\caption{$\epsilon$ vs. Num States and $\epsilon$ vs. Abstract Policy Value}
\end{figure}
